### 2013-09-22 manuscripts/reply/reply.tex
More work on text of reply.

\newpage
\noindent Recently, this journal has served as a venue for discussion of the
potential pitfalls of approximate Bayesian methods of comparative
phylogeographical model choice.
The discussion is centered around the approximate Bayesian model choice method,
\msb, which estimates the temporal distribution of divergences among
co-distributed pairs of taxa.
\citet{Oaks2012} published their findings that the method \msb can often be
biased towards inferring models of temporally clustered divergence times
among taxon pairs.
\citet{Hickerson2013} has published a response to this paper where they
present a model-averaging approach that they conclude circumvents the poor
behavior of the method revealved by \citet{Oaks2012}.
Both of these papers are largely in agreement.
In fact, \citet{Hickerson2013} reiterate a lot of the discussion of
\citet{Oaks2012} regarding the impact of broad uniform priors on Bayesian model
choice.
The main differences in their perspectives are centered around
(1) the means by which broad uniform priors cause the poor behavior of \msb,
and
(2) how to potentially ameliorate this issue.

\citet{Oaks2012} conclude the primary mechanism by which broad priors cause the
poor behavior of the method is likely the low marginal likelihoods of
parameter-rich models integrated over vast parameter space with low probability
of producing the data, yet relatively high prior density \citep[this is often
referred to as Lindley's paradox;][]{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of the method could be sound.
\citet{Hickerson2013} take a more pessimistic view of the bias, and suggest it
is intrinsic to \msb, i.e., the method's rejection algorithm is
inefficient and will be increasingly biased as the overall space of the model
increases, either as a function of the number of taxon pairs or the width of
the uniform priors on nuisance parameters.
They support their position by giving a probabilistic argument that focuses on
only one of the three prior models used by \citet{Oaks2012}.
We show that this argument is based on dubious assumptions, and does not
explain the bias of the method found in several analyses of \citet{Oaks2012}.
We reiterate several of the findings of \citet{Oaks2012} as well as present
results of additional analyses, which strongly suggest that Lindley's paradox
is playing a large role in the poor behavior of the method.

\citet{Oaks2012} suggest that more cogent prior probability distributions on
divergence models and nuisance parameters could mitigate the effect of
Lindley's paradox.
They also layout a set of simulation-based procedures for determining power,
accuracy, and robustness of the method given a dataset, and recommend any
application of \msb should be accompanied by such procedures, especially
if any biological conclusions are going to drawn from the results.
\citet{Hickerson2013} present an approximate Bayesian model-averaging approach
for accommodating uncertainty in selecting among empirically guided priors, and
champion the method as a means of avoiding the pitfalls raised by
\citet{Oaks2012}.
Unfortunately, we show that fundamental errors in this approach render some of
their results invalid and leave the remaining results difficult to interpret.
Furthermore, we follow the advice of \citet{Oaks2012} and present
simulation-based assessments of Hickerson et al.'s \citeyear{Hickerson2013}
approach.
Our results demonstrate that the method is biased and dangerous.
The approach merely provides another means by which the model can ``escape''
large parameter space, and the bias towards models with smaller space still
remains.
This bias can be dangerous and often excludes the true parameter space due to
the use of uniform priors.
Furthermore we discuss the potential theoretical and practical problems of
empirical Bayesian model choice.

@@

Each of the eight prior models used in the re-analysis by \citet{Hickerson2013}
has one of two priors on the mean population size of the descendant populations
of each taxon pair:
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ or
$\meanDescendantTheta{} \sim U(0.0005, 0.04)$ or
As described in \citet{Oaks2012}, the divergence time parameters of the model
implemented in \msb are scaled relative to a constant reference population
size, \myTheta{C}.
This reference population size is defined in terms of the upper limit on the
uniform prior on the mean population size of the descendant populations,
\meanDescendantTheta{}, such that for the prior $\meanDescendantTheta{} \sim
U(\uniformMin{\meanDescendantTheta{}},\uniformMax{\meanDescendantTheta{}})$,
$\myTheta{C} = \uniformMax{\meanDescendantTheta{}}/2$.
Thus, the model used by \citet{Hickerson2013} mixes two different units of
time.
In other words, some of their prior and posterior samples are in units of
$0.05/\mutationRate$ generations, whereas other are in units of
$0.02/\mutationRate$ generations.

The fact that their posterior samples are in different units makes the results
of \citet{Hickerson2013} difficult to interpret, and renders their
regression-adjusted results invalid; a fundamental assumption of regression is
that all of the values of the response variable are in the same units.
Thus, the results in section ``Improved Sampling Efficiency by Prior Weighting
Supports Asynchronous and Recent Divergence for the Philippines Vertebrate
Data'' and presented in Figure 2 of \citet{Hickerson2013} should be
disregarded.
The error is easily illustrated by re-plotting their results with the different
time units indicated (Figure~\ref{figJointPosteriorHickerson}.

@@

\section*{The dangers of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected''.
However, this is bit misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors (see their section ``Specifying and simulating the joint
prior'').
They detail how the being limited to uniform prior distributions necessitates
awkward broad priors to avoid excluding the truth, a priori.
What \citet{Hickerson2013} really mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing
both the prior sensitivity of the method and determining the power of \msb
under the ``best'' possible real-world conditions.
\citet{Oaks2012} discuss the potential dangers of taking an empirical Bayesian
model choice (see last paragraph of ``Assessing prior sensitivity of \msb''),
and we expand on this here by exploring the theoretical and practical
implications of using an empirical Bayes approach to model choice.

@@

This is an elegant method of updating our beliefs as data are accumulated.
However, this all hinges on the fact that the prior ($p(\myTheta{})$) is
defined for all possible parameters independently of the new data being
analyzed.
Any other datasets or external information can safely be used to inform our
beliefs about $p(\myTheta{})$.
However, if the data are used to both inform the prior and calculate the
posterior, the prior becomes conditional on the data, and Bayes' rule breaks
down.

Now, this is not to say that empirical Bayesian approaches not useful.
Quite the contrary.
Empirical Bayes is a well studied branch of Bayesian statistics that
has given rise to a many powerful inference methods.
It is true that empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and misshapen;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
Nevertheless, empirical Bayes methods are often a powerful means of parameter
estimation that display favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often display good frequentist coverage behavior
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is much more dubious.
In Bayesian model choice, the goal is usually not to estimate parameters, but
to estimate the relative probabilities of candidate models.
Unlike parameter estimates, posterior probabilities represent a summary of the
entire posterior distribution.
Thus, given that empirical Bayesian posterior distributions are not accurate,
there is no guarantee regarding the accuracy of probabilities summarized from
them.

This can be demonstrated with a simple, albeit contrived, example.
Let us say that principal investigator Mary and her new postdoc Will are
interested in the hypothesis that the mass of George Washington's periwig
renders the United States' quarter dollar unfair.
That is to say that our null hypothesis is that the probability of a US quarter
landing heads when tossed is less than 0.5 ($\theta < 0.5$).
They can certainly evaluate this hypothesis, they can have undergraduate
worker, Joe, flip the coin for them while the tabulate the results.
But being Bayesians, before they call Joe into the lab, they agree on a
prior probability to place on the set of all possible probabilities that
the quarter will land heads when it is flipped.
Given their prior knowledge that Joe moonlights as a magician, and is notorious
for performing coin and card tricks in the lab, they suspect there is a good
chance that Joe will use his slight-of-hand skills to replace their quarter
with one of his two-headed or two-tailed coins he has up his sleeve at all
times.
So, knowing that the beta distribution is the conjugate prior for a binomial
likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
(Figure~\ref{figCoinFlip}).

@@

If Joe's flips were a representative sample, Mary and Will's empirical Bayes
estimate might very well be a better estimator for the parameter \myTheta{}.
However, their empirical Bayes estimate of the probability of their hypothesis
is incorrect and biased.
This simple example shows how parameter estimation is fundamentally different
from estimating the probability of a model.
While empirical informed priors can be used to obtain well-behaved parameter
estimators, using them for model choice is much less certain.

\subsection*{Practical dangers of narrow uniform priors for Bayesian model
choice}
Given that \msb can be biased toward models with smaller parameter space, and
Hickerson et al.'s \citeyear{Hickerson2013} use of narrow, empirically informed
uniform priors on divergence times, we sought to determine whether such an
approach will often exclude the truth (i.e., the model-averaged posterior will
be dominated by models that excude the true values of parameters of the model).
We explored this possiblity in two ways.
First, we reanalyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
the truth.
If Lindley's paradox causes the method to prefer models with less parameter
space, we expect \msb will preferentially sample from this incorrect model
yielding a marginal posterior that is invalid (i.e., the model-averaged
posterior will be dominated by an incorrect model that excludes the truth).
Second, we generated simulated datasets for which the divergence times are
drawn form an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

The empirically guided, narrowest prior of \citet{Hickerson2013} ($\divt{} \sim
U(0,0.1)$) likely excludes the true values for at least some of the Philippine
taxa.
They set this prior to match the 95\% highest posterior density (HPD) interval for
the mean divergence time estimated under one of the priors used by
\citet{Oaks2012} (see Table 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it seems odd to set this as the prior, as many of the taxon pairs
likely diverged at times older than the upper limit.
Furthermore, the prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two prior analyses (under these
priors the 95\% HPD is approximately 0.3--0.6; see Table~6 of
\citet{Oaks2012}).

For our re-analysis of the Philippines dataset we used the model-averaging
approach of \citet{Hickerson2013}, but with different prior models to avoid
mixing time units. We used five priors, all of which had priors on population
sizes of $\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and
$\ancestralTheta{} \sim U(0.0001, 0.05)$.
Following \citet{Hickerson2013}, each of these priors had the following
priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
For our prior, we simulated $1\e6$ random samples from each of the models
for a total sample of $5\e6$.
For each model, we retained the 10,000 samples with the smallest Euclidean
distance from the observed summary statistics, standardizing the statistics
using the prior means and standard deviations of the given model.
We then retained the 10,000 samples with the smallest Euclidean distance from
the observed summary statistics, this time standardizing the statistics using
the prior means and standard deviations across all five models.
We then repeated this analysis twice, replacing the $M_1$ with
$M_1A$ and $M_1B$, which differ only by having priors on divergence
times of $\divt{} \sim U(0, 0.01)$ and $\divt{} \sim U(0, 0.001)$,
respectively.
While we suspect the prior of $\divt{} \sim U(0, 0.1)$ used by
\citet{Hickerson2013} likely excludes the true divergence times of
at least some of the 22 taxa, we are nearly certain that these
narrower priors are incorrect and exclude the truth.

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the methods bias towards models with smaller parameter space,
but rather allow it to manifest in a very dangerous way.
The method strongly prefers the prior model with the narrowest distribution on
divergence times across all three of our analyses, even when this model is
almost certainly incorrect and excludes the true divergence times of the
Philippine taxa.
Unfortunately, ``checking'' the priors by plotting the summary statistics from
1000 random samples of each prior model along the first two orthogonal axes of
a principle component analysis, as recommended by \citet{Hickerson2013},
provides no warning of a problem (Figure~\ref{figPCA}.
Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude at least some of
the 22 true divergence times, making their results difficult to interpret.

To better quantify the propensity of Hickerson et al.'s
\citeyear{Hickerson2013} approach to exclude the truth, we simulated
1000 pseudo-observed datasets in which the divergence times for the
22 population pairs are drawn randomly from an exponential distribution
with a mean of 0.5 ($\divt{} \sim Exp(2)$). All other parameters were
identically distributed as in the $M_1$--$M_5$ models.
We then repeated the analysis described above, using $5\e6$ prior samples from
$M_1$, $M_2$, $M_3$, $M_4$, and $M_5$, and retaining 1,000 posterior samples
for each of the 1,000 pseudo-observed datasets.

\highLight{Add how we determined exclusion.}
Our results show that the model-averaging approach of \citet{Hickerson2013}
excludes the true values of parameters in 97\% of the replicates (90\% with
GLM-regression adjustment), excluding up to 21 of the 22 true divergence times
(Figure~\ref{figExclusionSimTau}.
Furthermore, the posterior probability of excluding at least one true parameter
value is very high in nearly all of the replicates
(Figure~\ref{figExclusionSimProb}).
We used a Bayes factor (comparing models that exclude the truth to those that
do not) calculated for each replicate of greater than 10 as strong support for
excluding the truth.
With that criterion, 66\% of the replicats (87\% with GLM-regression adjustment)
strongly support the exclusion of true values (Figure~\ref{figExclusionSimProb}).

The results of our empirical and simulation-based analyses clearly demonstrate
the danger of using narrow, empirically guided priors in a Bayesian
model-averaging framework \ldots

\subsection*{Final thought on EB}
Given all of the theoretical and practical issues with empirical Bayes
approaches to Bayesian model choice discussed in the proceeding sections, it is
quite clear why one should use caution before overly criticizing an
investigators choice of priors after having seen the posterior.
In a strictly Bayesian world, this is cheating.
As discussed by \citet{Oaks2012}, prior to analysing the data, there was a large
amount of uncertainty regarding the divergence times of the 22 population pairs
under study.
Two the these pairs represent distinct species, and the taxonomy of many groups
in the Philippines has repeatedly been shown to mask deeply divergent lineages
\citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
Siler2011,Siler2012,RafeStuart2012}.
\highLight{Any new stuff to add to this list of citations?}.
\citet{Oaks2012} also discuss how the sole use of uniform priors in \msb makes
it very difficult for investigators to express their prior uncertainty without
putting a lot of prior density in regions of improbable parameter space.
The alternative, as shown above, is to risk excluding the truth before even
conducting the analysis.

\section*{Our power analysis}
\citet{Hickerson2013} did not conduct a power analysis to accompany their
inference of clustered divergences from the Philippines data (as recommended by
\citet{Oaks2012}).
Thus, we perform perform simulation-based power analyses to explore the
power of the approximate Bayesian model-averaging approach championed
by \citet{Hickerson2013}.

Following \citet{Oaks2012}, we simulated 1000 pseudo-replicate datasets with
\divt{} for each of the 22 population pairs randomly drawn from a uniform
distribution, $U(0, \divt{max})$, where \divt{max} was set to: 0.2, 0.4, 0.6,
0.8, 1.0, and 2.0, in \globalcoalunit generations.
All other parameters were identically distributed as the prior.
Following \citet{Hickerson2013} (but avoiding mixing time units), we used five
priors, all of which had priors on population sizes of $\meanDescendantTheta{}
\sim U(0.0001, 0.1)$ and $\ancestralTheta{} \sim U(0.0001, 0.05)$.
Each of these priors had the following priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
For our prior, we simulated $1\e6$ random samples from each of the models
for a total sample of $5\e6$.
For each pseudo-replicate dataset, we retained the 1000 samples from each prior
model with the smallest Euclidean distance from the replicates' summary
statistics, standardizing the statistics using the prior means and standard
deviations of the given model.
Then, for each replicate, we retained the 1000 samples with the smallest
Euclidean distance from the pseudo-observed summary statistics, this time
standardizing the statistics using the prior means and standard deviations
across all five models.
In total, we analyzed 6000 replicate datasets, retaining 1000 model-averaged
posterior samples from each of them.

>>>>

\newpage
\noindent Recently, this journal has served as a venue for discussion of the
potential pitfalls of approximate Bayesian methods of comparative
phylogeographical model choice.
The discussion is centered around the approximate Bayesian model choice method,
\msb, which estimates the temporal distribution of divergences among
co-distributed pairs of taxa \citep{Huang2011}.
\citet{Oaks2012} published their findings that the method \msb can often be
biased towards inferring models of temporally clustered divergence times among
taxon pairs.
\citet{Hickerson2013} has published a response to this paper where they
present a model-averaging approach that they conclude circumvents the poor
behavior of the method revealed by \citet{Oaks2012}.
Both of these papers are largely in agreement.
In fact, \citet{Hickerson2013} reiterate a lot of the discussion of
\citet{Oaks2012} regarding the impact of broad uniform priors on Bayesian model
choice.
The main differences in their perspectives are centered around
(1) the mechanism by which broad uniform priors cause the poor behavior of
\msb, and
(2) how to potentially ameliorate this issue.

Regarding the mechanism behind the poor behavior of the method,
\citet{Oaks2012} suggest the primary cause is likely the low marginal
likelihoods of parameter-rich models integrated over vast parameter space with
low probability of producing the data, yet relatively high prior density
\citep[this is often referred to as Lindley's paradox;][]{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of the method could be sound.
\citet{Hickerson2013} take a more pessimistic view of the bias, and suggest it
is intrinsic to \msb.
They conclude the method's rejection algorithm is inefficient and will be
increasingly biased as the overall space of the model increases, either as a
function of the number of taxon pairs or the width of the uniform priors on
nuisance parameters.
They support their position by giving a probabilistic argument that focuses on
only one of the three prior models used by \citet{Oaks2012}.
We show that this argument is based on dubious assumptions, and does not
explain the bias of the method found in several analyses of \citet{Oaks2012}.
Furthermore, we reiterate several of the findings of \citet{Oaks2012} as well
as present results of additional analyses, which strongly suggest that
Lindley's paradox is playing a large role in the poor behavior of the method.

As for how to mitigate the bias, \citet{Oaks2012} suggest that more cogent
prior probability distributions on divergence models and nuisance parameters
could reduce the effect of Lindley's paradox.
They also layout a set of simulation-based procedures for determining power,
accuracy, and robustness of the method given a dataset, and recommend any
application of \msb should be accompanied by such procedures, especially
if any biological conclusions are going to drawn from the results.
\citet{Hickerson2013} present an approximate Bayesian model-averaging approach
for accommodating uncertainty in selecting among empirically guided priors, and
champion the method as a means of avoiding the pitfalls raised by
\citet{Oaks2012}.
Unfortunately, we show that fundamental errors in this approach render some of
their results invalid and leave the remaining results difficult to interpret.
Furthermore, we follow the advice of \citet{Oaks2012} and present
simulation-based assessments of Hickerson et al.'s \citeyear{Hickerson2013}
approach.
Our results demonstrate that the method is biased and dangerous.  The approach
merely provides another means by which the model can ``escape'' large parameter
space, and bias towards smaller models remains.
This manifestation of the bias can be dangerous and often excludes the true
parameter space due to the use of uniform priors.
Furthermore we discuss the potential theoretical and practical problems of
empirical Bayesian model choice, which is encouraged by \citet{Hickerson2013}
without any mention of its potential complications.

@@

Each of the eight prior models used in the re-analysis by \citet{Hickerson2013}
has one of two priors on the mean population size of the descendant populations
of each taxon pair:
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ or
$\meanDescendantTheta{} \sim U(0.0005, 0.04)$ or
As described in \citet{Oaks2012}, the divergence time parameters of the model
implemented in \msb are scaled relative to a constant reference population
size, \myTheta{C}.
This reference population size is defined in terms of the upper limit on the
uniform prior on the mean population size of the descendant populations,
\meanDescendantTheta{}, such that for the prior $\meanDescendantTheta{} \sim
U(\uniformMin{\meanDescendantTheta{}},\uniformMax{\meanDescendantTheta{}})$,
$\myTheta{C} = \uniformMax{\meanDescendantTheta{}}/2$.
Thus, the model used by \citet{Hickerson2013} mixes two different units of
time.
In other words, some of their prior and posterior samples are in units of
$0.05/\mutationRate$ generations, whereas others are in units of
$0.02/\mutationRate$ generations.

The fact that their posterior samples are in different units makes the results
of \citet{Hickerson2013} difficult to interpret, and renders their
regression-adjusted results invalid; a fundamental assumption of regression is
that all of the values of the response variable are in the same units.
Thus, the results in sections ``Using ABC Model Comparison to Weight
Alternative Priors for the Philippine Vertebrate Data'' and ``Improved Sampling
Efficiency by Prior Weighting Supports Asynchronous and Recent Divergence for
the Philippines Vertebrate Data'' and presented in Figure 2 of
\citet{Hickerson2013} should be disregarded.
The error is easily illustrated by re-plotting their results with the different
time units indicated (Figure~\ref{figJointPosteriorHickerson}.

@@

\section*{The dangers of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected''.
However, this is bit misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors (see their section ``Specifying and simulating the joint
prior'').
They detail how being limited to uniform prior distributions in \msb
necessitates awkward broad priors to avoid excluding the truth, a priori.
What \citet{Hickerson2013} really mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing
both the prior sensitivity of the method and determining the power of \msb
under real-world conditions with highly informative priors.
\citet{Oaks2012} discuss the potential dangers of taking an empirical Bayesian
approach to model choice (see last paragraph of ``Assessing prior sensitivity
of \msb''), and we expand on this here by exploring both the theoretical and
practical implications of using empirically informed priors for Bayesian
model choice.

@@

This is an elegant method of updating our beliefs as data are accumulated.
However, this all hinges on the fact that the prior ($p(\myTheta{})$) is
defined for all possible parameter values independently of the new data being
analyzed.
Any other datasets or external information can safely be used to inform our
beliefs about $p(\myTheta{})$.
However, if the same data are used to both inform the prior and calculate the
posterior, the prior becomes conditional on the data, and Bayes' rule breaks
down.

This is not to say that empirical Bayesian approaches not useful.
Quite the contrary.
Empirical Bayes is a well studied branch of Bayesian statistics that
has given rise to a many powerful inference methods.
It is true that empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and misshapen;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
Nevertheless, empirical Bayes methods can provide a powerful means of parameter
estimation.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often exhibit good frequentist properties
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is much more uncertain.
In Bayesian model choice, the goal is not to estimate parameters, but to
estimate the relative probabilities of candidate models.
Unlike parameter estimates, posterior probabilities represent a summary of the
entire posterior distribution.
Thus, given that empirical Bayesian posterior distributions are not accurate,
there is no guarantee regarding the accuracy of probabilities summarized from
them.

This can be demonstrated with a simple, albeit contrived, example.
Let us say that principal investigator Mary and her new postdoc Will are
interested in the hypothesis that the mass of George Washington's periwig
renders the quarter dollar of the United States unfair.
That is to say that their null hypothesis is that the probability of a US
quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
They can certainly evaluate this hypothesis, they can have undergraduate
worker, Joe, flip the coin for them while the tabulate the results.
But being Bayesians, before they call Joe into the lab, they agree on a
prior probability to place on the set of all possible probabilities that
the quarter will land heads when it is flipped.
Given their prior knowledge that Joe moonlights as a magician, and is notorious
for performing coin and card tricks in the lab, they suspect there is a good
chance that Joe will use his slight-of-hand skills to replace their quarter
with one of his two-headed or two-tailed coins he has up his sleeve at all
times.
So, knowing that the beta distribution is the conjugate prior for a binomial
likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
(Figure~\ref{figCoinFlip}).

@@

If Joe's flips were a representative sample, Mary and Will's empirical Bayes
estimate might very well be a better point estimate for the parameter
\myTheta{}.
However, their empirical Bayes estimate of the probability of their hypothesis
is incorrect and biased.
This simple example shows how parameter estimation is fundamentally different
from estimating the probability of a model.
While empirical informed priors can be used to obtain well-behaved parameter
estimators, using them for model choice is much less certain.

\subsection*{Practical dangers of narrow uniform priors for Bayesian model
choice}
We were alarmed when we saw the results of the model-averaging results
presented in \citet{Hickerson2013}.
Their results strongly favored the models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This concerned us because the narrowest prior of \citet{Hickerson2013}
($\divt{} \sim U(0,0.1)$) likely excludes the true divergence times for at
least some of the Philippine taxa.
They set this prior to match the 95\% highest posterior density (HPD) interval for
the mean divergence time estimated under one of the priors used by
\citet{Oaks2012} (see Table 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it seems odd to set this as the prior, because many of the taxon pairs
are expected to have diverged at times older than the upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
Thus, when we saw the results of \citet{Hickerson2013} we suspected that
Lindley's paradox was again biasing the method toward models with smaller
parameter space, and as a consequence was biasing the method toward models
that exclude the truth (i.e., the model-averaged posterior will
be dominated by models that exclude the true values of parameters of the model).

We explored the propensity of the model-averaging approach of
\citet{Hickerson2013} to exclude the truth in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If Lindley's paradox causes the method to prefer models with less parameter
space, we expect \msb will preferentially sample from this incorrect model
yielding a marginal posterior that is incorrect (i.e., the model-averaged
posterior will be dominated by an incorrect model that excludes the truth).
Second, we generated simulated datasets for which the divergence times are
drawn form an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

For our re-analysis of the Philippines dataset we used the model-averaging
approach of \citet{Hickerson2013}, but with different prior models to avoid
their error of mixing time units.
We used five priors, all of which had priors on population sizes of
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and $\ancestralTheta{} \sim
U(0.0001, 0.05)$.
Following \citet{Hickerson2013}, each of these priors had the following
priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
For our prior, we simulated $1\e6$ random samples from each of the models
for a total sample of $5\e6$.
For each model, we retained the 10,000 samples with the smallest Euclidean
distance from the observed summary statistics, standardizing the statistics
using the prior means and standard deviations of the given model.
From the remaining 50,000 samples, we then retained the 10,000 samples with the
smallest Euclidean distance from the observed summary statistics, this time
standardizing the statistics using the prior means and standard deviations
across all five models.
We then repeated this analysis twice, replacing the $M_1$ with
$M_1A$ and $M_1B$, which differ only by having priors on divergence
times of $\divt{} \sim U(0, 0.01)$ and $\divt{} \sim U(0, 0.001)$,
respectively.
While we suspect the prior of $\divt{} \sim U(0, 0.1)$ used by
\citet{Hickerson2013} likely excludes the true divergence times of at least
some of the 22 taxa, we are nearly certain that these narrower priors are
incorrect and exclude most, if not all, of the divergence times of the
Philippine taxa.

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the methods bias towards models with smaller parameter space,
but rather allows it to manifest in a very dangerous way.
The method strongly prefers the prior model with the narrowest distribution on
divergence times across all three of our analyses, even when this model is
almost certainly incorrect and excludes the true divergence times of the
Philippine taxa.
Unfortunately, ``checking'' the priors by plotting the summary statistics from
1000 random samples of each prior model along the first two orthogonal axes of
a principle component analysis, as recommended by \citet{Hickerson2013},
provides no warning of a problem (Figure~\ref{figPCA}.
Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude at least some of
the 22 true divergence times, making their results difficult to interpret
(in addition to the error of time units).

To better quantify the propensity of Hickerson et al.'s
\citeyear{Hickerson2013} approach to exclude the truth, we simulated
1000 pseudo-observed datasets in which the divergence times for the
22 population pairs are drawn randomly from an exponential distribution
with a mean of 0.5 ($\divt{} \sim Exp(2)$). All other parameters were
identically distributed as the $M_1$--$M_5$ models.
We then repeated the analysis described above, using $5\e6$ prior samples from
$M_1$, $M_2$, $M_3$, $M_4$, and $M_5$, and retaining 1000 posterior samples
for each of the 1000 pseudo-observed datasets.

\highLight{Add how we determined exclusion.}
Our results show that the model-averaging approach of \citet{Hickerson2013}
excludes the true values of parameters in 97\% of the replicates (90\% with
GLM-regression adjustment), excluding up to 21 of the 22 true divergence times
(Figure~\ref{figExclusionSimTau}.
Furthermore, the posterior probability of excluding at least one true parameter
value is very high in nearly all of the replicates
(Figure~\ref{figExclusionSimProb}).
We used a Bayes factor (comparing models that exclude the truth to those that
do not) calculated for each replicate of greater than 10 as strong support for
excluding the truth.
With this criterion, 66\% of the replicates (87\% with GLM-regression adjustment)
strongly support the exclusion of true values (Figure~\ref{figExclusionSimProb}).

The results of our empirical and simulation-based analyses clearly demonstrate
the danger of using narrow, empirically guided uniform priors in a Bayesian
model-averaging framework.
This is especially dangerous \msb, which has already been demonstrated to be
biased away from models with more parameter space.
The consequence of this approach is a high risk of obtaining a model-averaged
posterior estimate that is heavily weighted toward incorrect models that
exclude true values of model parameters.

\subsection*{Final thoughts on empirical priors in Bayesian model choice}
Given all of the theoretical and practical issues with empirical Bayes
approaches to Bayesian model choice discussed in the proceeding sections, it is
quite clear why one should use caution before overly criticizing an
investigator's choice of priors after having seen the resulting posterior.
In a strictly Bayesian world, this is cheating.
As discussed by \citet{Oaks2012}, prior to analysing the data, there was a large
amount of uncertainty regarding the divergence times of the 22 population pairs
under study.
Two the these pairs represent distinct species, and the taxonomy of many groups
in the Philippines has repeatedly been shown to mask deeply divergent lineages
\citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
Siler2011,Siler2012,RafeStuart2012}.
\highLight{Any new stuff to add to this list of citations?}.
\citet{Oaks2012} also discuss how the sole use of uniform priors in \msb makes
it very difficult for investigators to express their prior uncertainty without
putting a lot of prior density in regions of improbable parameter space.
The alternative, as shown above, is to risk excluding the truth before
performing the analysis.

\section*{Assessing the power of the model-averaging approach of
    \citet{Hickerson2013}}
\citet{Hickerson2013} did not conduct a power analysis to accompany their
inference of clustered divergences from the Philippines data (as recommended by
\citet{Oaks2012}).
Thus, we perform simulation-based power analyses to explore the power of the
approximate Bayesian model-averaging approach championed by
\citet{Hickerson2013}.
